\documentclass[12pt]{article}

% set margins and spacing
\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\linespread{1.0}

% load miscellaneous packages
\usepackage{csquotes}
\usepackage[american]{babel}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding,times, verbatim,bm,pifont,pdfsync,setspace,natbib}

% enable hyperlinks and table of contents
\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true,hyperfootnotes=false]{hyperref}



\begin{document}
\title{Tariffs}
% add a fourth name if you have four team members; fill in at least first names below
\author{Kiana\thanks{Syracuse University, Economics Department. Email: } \and Betsy\thanks{abc} \and Giovanni\thanks{abc}\and Lucia\thanks{abc}}
\date{\vskip-.1in \today}
\maketitle

\vskip.3in

\section {Question}  \label{sec:question}



{How do taxes on goods and services relate to tariffs in developed countries? How does the relationship depend on a developed country’s GDP and its trade policies?
\section{Data Overview}  \label{sec:literature}

20 Year time period. Utilize firm-level data from WITS 
(World Integrated Trade Solution).https://wits.worldbank.org/

\subsection{Data Set 1: Trade relationship between taxes on consumption and international taxes (tariffs) of developed countries}
\begin{itemize}
  \item What is the source of the data?: WITS 
  \item How was it generated? Public reports compiled by the following organizations: WITS' TRAINS Tariff Measures and Preference Beneficiaries, UNCTAD, UN Comtrade and WTO IDB.
  \item What is the coverage of the data?: Developed Countries 
    \begin{itemize}
        \item *Time series (and time period) or cross-sectional data? What years?: 2001-2020
        \item *Unit of analysis / frequency of data What kind of observations: Developed countries with relatively high GDP per Capita
        \item Scope: 20 Developed countries- Ireland, United Arab Emirates, Netherlands, Austria, Sweden, Belgium, Germany, United States, Hong Kong, Singapore, South Korea, Turkey, Japan, Australia, Israel, Canada, United Kingdom, Norway, and Switzerland
        
    \end{itemize}
  \item Number of variables: 3 \begin{itemize}
        \item Types of variables: Economic Variables- GDP, Consumption Tax Rate, International Tax Rate 
    \end{itemize}
  \item *How many observations? How many observations total? 20 countries over 20 years for a total of 400 observations.
\end{itemize}

\section{Data Acquisition}
\label{sec:theory}
\subsection{WITS Country TimeSeries Exports of Goods and Services as Percent of GDP of Ireland, United Arab Emirates, Netherlands, Austria, Sweden, Belgium, Germany, United States, Hong Kong, Singapore, South Korea, Turkey, Japan, Australia, Israel, Canada, United Kingdom, Norway, and Switzerland from 2001-2020}
\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
        Country Name & Indicator Name & Years \\ \hline
        Australia & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Austria & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Belgium & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Canada & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        France & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Germany & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Hong Kong, China & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Ireland & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Israel & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Japan & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Korea, Rep. & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Netherlands & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Norway & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Singapore & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Sweden & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Switzerland & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Turkey & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United Arab Emirates & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United Kingdom & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United States & Exports of goods and services (\% of GDP) & 2001-2020 \\ \hline
    \end{tabular}
\end{table}
 Access to Excel document and country time series table: Local Excel File
\subsection{WITS Country TimeSeries Imports of Goods and Services as Percent of GDP of Ireland, United Arab Emirates, Netherlands, Austria, Sweden, Belgium, Germany, United States, Hong Kong, Singapore, South Korea, Turkey, Japan, Australia, Israel, Canada, United Kingdom, Norway, and Switzerland from 2001-2020}

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
        Country Name & Indicator Name & Years \\ \hline
        Australia & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Austria & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Belgium & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Canada & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        France & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Germany & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Hong Kong, China & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Ireland & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Israel & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Japan & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Korea, Rep. & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Netherlands & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Norway & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Singapore & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Sweden & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Switzerland & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        Turkey & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United Arab Emirates & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United Kingdom & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
        United States & Imports of goods and services (\% of GDP) & 2001-2020 \\ \hline
    \end{tabular}
\end{table}

  Access to Excel document and country time series table: Local Excel File
\begin{itemize}
  \item Export of Value Added Summary Data: Access online database and select country / year for data: https://wits.worldbank.org/analyticaldata
/evad/country/hkg/Year/2014/Summary - Copy / paste the URL to view the top five exporting sectors of all twenty countries when considering forward links or backward links as a share of total domestic value added that is exported, and the top five export-intensive sectors as a share of gross exports for years included. The sector's value added is embedded as inputs in other sectors' exports and the value added embedded in the sector's exports from all other sectors-
\end{itemize}
\begin{itemize}
  \item Trade Summary Data: Access online database and select country / year for data: 
https://wits.worldbank.org/
CountryProfile
/en/Country/HKG/Year/2001/Summarytext
-Copy/paste the url to view all twenty countries’ trade summary including Overall Exports and Imports, top 5 Export and Import partners, Top 5 Products Exports imports at HS 6 digit level, Exports and imports of products by stages of processing as percent of total export or import, Tariffs imposed, Key Development Indicators, Trade Indicators-
\end{itemize}

\section{Data Manipulation}
\label{sec:data}

What steps have you taken / do you plan to take to get the data ready for analysis? 
\begin{itemize}
    \item Examples: checking for outliers; dropping some observations you don't need; investigating something you've already noticed that doesn't make sense.
    \item If you've already done some work, where are the files and documentation for that work?
\end{itemize}

\section{Linking Datasets}
\label{sec:discussion}

How you will link different data sets together (if you'll need to)
\begin{itemize}
    \item What variable(s) in each dataset will you use to merge the datasets together?
    \item Example: We will merge Dataset A with GDP for each country with Dataset B that has manufacturing employment for each country across years. In Dataset A, these variables are called \textit{year} and \emph{country}; Dataset B calls the year variable \emph{yr} and the country variable \emph{name}.
\end{itemize}


\section{Key Variables}
\label{sec:result}

\begin{itemize} *Which variables did you name in the reading quiz?
    \item Exports of goods and services (\% of GDP)
    \item Imports of goods and services (\% of GDP)
    \item Gross Domestic Product (GDP)
    \item Gross National Income (GNI)
    \item Trade balance
    \item Top 5 Export and Import Partners
    \item Top 5 Products Exports and Imports (HS 6-digit level)
    \item Exports and Imports by stage of processing (e.g., raw materials, intermediates, finished goods)
    \item Tariffs imposed
    \item Key Development Indicators
    \item Export of Domestic Value Added by sector
    \item Value added used in other countries’ exports
    \item Foreign value added in domestic exports
    \item Top 5 Export-Intensive Sectors as a share of gross exports
\end{itemize}






\end{document}